Classless Java

### 2016-03-24 OOPSLA16/sections/CaseStudy.tex
add references
Some spacing tweking.
Case study

\section{Case Studies}
In this section we conduct \numOfCaseStudies case studies which reveal various
advantages of using the \mixin annotation. The first case study provides a
simple way to solve the Expression Problem while supporting multiple,
independent extensions in Java.  The second case study shows how to model an
embedded DSL for SQL languages with fluent interfaces. The third
case study models a simple game, and compares our implementation with an
existing one, showing that the amount of code is reduced significantly using \mixin.
Finally, the fourth one refactors an interpreter, showing that our approach  
benefits modularity and scales to larger and real code base.

\subsection{A Trivial Solution to the Expression Problem with Object Interfaces}

@@

\subsection{Refactoring an Interpreter}
The last case study applies our approach to a slightly larger code base of an
interpreter for a Lisp-like language
\lstinline{Mumbler}\footnote{https://github.com/cesquivias/mumbler/tree/master/simple},
which is created for tutorial purpose of Truffle. Keeping a balance between
simplicity and useful features, \lstinline{Mumbler} contains numbers, booleans,
lists (encoding function calls and special forms such as if-expression, lambdas,
etc). In the original code base, only one operation \texttt{eval} is
supported. We add one more operation \texttt{print} to the code base. Then we
modularize the code using our techniques to convert as many classes into
interfaces, separate out \texttt{eval} and \texttt{print} operation then combine
them. Although the code size is slightly increased (by 2.2\% SLOC), the
modularity is greatly increased.

>>>>

\section{Applications and Case Studies}

This section illustrates applications and larger case studies for
Classless Java. The first application shows how a useful pattern,
using multiple inheritance and type-refinement, can be conviniently
encoded in Classless Java. The second application. shows how to model an
embedded DSL based on fluent APIs. The two larger case studies, take 
existing projects and refactor them into Classless Java. The first
case study shows a significant reduction in code size, while the
second case study maintains the same amount of code, but increases 
modularity.

\subsection{The Expression Problem with Object Interfaces}

@@

\subsection{Refactoring an Interpreter}
The last case study applies our approach to a slightly larger code base of an
interpreter for a Lisp-like language
\lstinline{Mumbler}\footnote{https://github.com/cesquivias/mumbler/tree/master/simple},
which is created for tutorial purpose of Truffle~\cite{wurthinger2013one}. Keeping a balance between
simplicity and useful features, \lstinline{Mumbler} contains numbers, booleans,
lists (encoding function calls and special forms such as if-expression, lambdas,
etc). In the original code base, only one operation \texttt{eval} is
supported. We add one more operation \texttt{print} to the code base. Then we
modularize the code using our techniques to convert as many classes into
interfaces, separate out \texttt{eval} and \texttt{print} operation then combine
them. Although the code size is slightly increased (by 2.2\% SLOC), the
modularity is greatly increased.
